Trans-dimensional Bayesian Inference and Nested Sampling

### 2014-08-10 Documents/Talk/content.tex
Marginalisation figure

\begin{frame}[t]{Bayesian Computation}
To explore the posterior distribution, the Metropolis algorithm is a standard
technique:

\begin{itemize}
\item Start at some point $\theta$ in the hypothesis space.
\item Loop\\
$\{$
  \begin{itemize}
  \item Generate {\bf proposal} from some distribution $q(\theta' | \theta)$
  (e.g. slightly perturb the current position).
  \item With probability$^*$ $\alpha = \min\left(1, \frac{p(\theta')p(D|\theta')}{p(\theta)p(D|\theta)}\right)$, accept the proposal (i.e. replace $\theta$ with $\theta'$).
  \item Otherwise, stay in the same place.
  \end{itemize}
$\}$
\end{itemize}

>>>>

\begin{frame}[t]{Computation: Markov Chain Monte Carlo}
To explore the posterior distribution, the Metropolis algorithm is a standard
technique:

\begin{itemize}
\item Start at some point $\theta$ in the hypothesis space.
\item Loop\\
$\{$
  \begin{itemize}
  \item Generate {\bf proposal} from some distribution $q(\theta' | \theta)$
  (e.g. slightly perturb the current position).
  \item With probability$^*$ $\alpha = \min\left(1, \frac{p(\theta')p(D|\theta')}{p(\theta)p(D|\theta)}\right)$, accept the proposal (i.e. replace $\theta$ with $\theta'$).
  \item Otherwise, stay in the same place.
  \end{itemize}
$\}$
\end{itemize}
\end{frame}

\begin{frame}[t]{What sampling gives us}
\begin{columns}[T]
\begin{column}{0.4\textwidth}
  \begin{itemize}
  \setlength{\itemsep}{20pt}
  \item {\bf Marginalisation} becomes trivial
  \item We can quantify all uncertainties we might be interested in
  \end{itemize}
\end{column}
\hfill
\begin{column}{0.55\textwidth}
  \includegraphics[scale=0.25]{marginalisation.pdf}
\end{column}

\end{columns}
\end{frame}
